Research highlights

### 2021-04-24 letter/responseToReviewers.tex

Since the statistics or long-term averages of pseudo-orbits and shadowing orbits are close, we expect that the pseudoorbit (the numerical solution $\hat{x}(t)$) is also not guaranteed to be statistically consistent.

As you rightly pointed out, in some scenarios, the pseudo-orbits may in fact inhabit the same or almost the same attractor. In other words, the attractor, or the set that all orbits of Eq. \ref{eqn:true} converge to asymptotically, may be identical or very close to that of Eq. \ref{eqn:numerical}. However, the probability distribution of an ensemble of orbits on the attractor, which is proportional to the amount of time almost every orbit spends in each portion of the attractor, are not guaranteed to be the same for the two models. This is the main argument in the paper.

We hope that this clarifies our position: we refute the belief that, due to shadowing, numerical solutions, which are considered to be pseudo-orbits that are close to true orbits, are also capable of modeling the true long-term behavior of a chaotic system. We support our claim by proving that shadowing orbits, despite being true orbits, are not representative of almost every orbit of the system: they can have atypical statistical behavior.

Thank you again for raising this question! As you point out, we have only proved that numerical solutions are not guaranteed to produce the true long-term/statistical behavior, and not that numerical solutions are always statistically inconsistent (after all, some shadowing trajectories are physical -- e.g. section 4.1). However, several references strengthen the observation of statistical inconsistency of numerics. The new references sent by Reviewer 1 that introduce clean numerical simulation, which are now cited in the revised manuscript, and the previously cited references (Sauer et al, which takes an analytical approach) in section 5 all observe that numerical solutions produce statistical/long-term inconsistencies. We have added more explanation (in \reviewerTwo{blue}) to clarify this point in section 5. 
\vspace{0.2in}

### 2021-05-06 highlights.tex
highlights modify and change supp to appendix

\documentclass[12pt]{article}
\title{Research highlights}
\begin{document}
\maketitle
\begin{itemize}
\item This paper highlights through rigorous examples that numerical solutions of chaotic dynamical systems are not guaranteed to produce the correct statistics or long-term behavior;
\item We show through examples that it is theoretically possible to significantly alter the statistics of a chaotic system by minor parameter perturbations.
\item The nonphysicality of shadowing orbits also implies that methods to compute parametric derivatives of statistics in chaotic systems, based on shadowing, may produce incorrect results.
\end{itemize}
\end{document}

>>>>

\documentclass[12pt]{article}
\title{Research highlights}
\begin{document}
\maketitle
\begin{itemize}
\item Shadowing orbits may not be typical orbits or physical solutions
\item This atypicality implies shadowing-based sensitivity can be biased.
\item Numerical solutions of chaotic dynamical systems can be statistically inconsistent;
\item Minor parameter changes can significantly alter the statistics of a chaotic system.

\end{itemize}
\end{document}
